Charting form template

### 2024-10-26 doc/charting/_template.qmd
docs: :pencil2: very minor edits to template, most format and one typo

::: content-hidden
fill in one form per paper. Name the form according to first author and
year like this: "Turoman-2022". Copy-paste the information from the
full-text review below.
:::

# title of publication

@@

### Specific tools mentioned - their function - where in the researh process used

::: content-hidden
For instance: "OSF - pre-registration - planning". You can mention
multiple tools. Just make another bullet.

>>>>

::: content-hidden
Fill in one form per paper. Name the form according to first author and
year like this: "Turoman-2022". Copy-paste the information from the
full-text review below.
:::

# Title of publication

@@

### Specific tools mentioned; their function; where in the research process used

::: content-hidden
For instance: "OSF; pre-registration; planning". You can mention
multiple tools. Just make another bullet.
